Bayesian inference of prehistoric demography from multiple proxies: a case study from the Swiss plateau

### 2022-05-23 manuscript/paper.Rmd
Clarify our approach as an extension of SPD

The 'dates as data' or summed radiocarbon approach has contributed greatly to our understanding of prehistoric demography, but it is not without its critics [@attenbrow_hiscock_2015, @carleton_groucutt_2020]. While the methodology continues to evolve and to an extent accommodate these critiques [@crema_review_2022], there are certain essential problems that cannot be solved with methodological refinements in this area alone [@french_manifesto_2021, @schmidt_approaching_2021].<!-- [JR] What problems? -->

>>>>

The 'dates as data' or summed radiocarbon approach has contributed greatly to our understanding of prehistoric demography, but it is not without its critics [@attenbrow_hiscock_2015, @carleton_groucutt_2020]. While the methodology continues to evolve and address these critiques [@crema_review_2022], it remains subject to certain fundamental problems common to all approaches that rely on a single proxy [@french_manifesto_2021, @schmidt_approaching_2021]. We believe that these problems cannot be overcome by methodological refinements in this area alone. Instead, the Bayesian approach we develop in this paper offers a robust, quantitative methodology for inferring prehistoric population dynamics from multiple proxies, including summed radiocarbon.
